\documentclass[10pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{enumitem}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage{hyperref}
\geometry{margin=1in}

\newif\ifdarkmode
\darkmodefalse  % Default to light mode

% Color definitions based on mode
\ifdarkmode
  \definecolor{background}{HTML}{121212}
  \definecolor{text}{HTML}{FFFFFF}
  \definecolor{accent}{HTML}{BB86FC}
\else
  \definecolor{background}{HTML}{FFFFFF}
  \definecolor{text}{HTML}{000000}
  \definecolor{accent}{HTML}{6200EE}
\fi

\newcommand\myname{Gustavo Luís Luchetti}

\pagecolor{background}
\color{text}
\setlength{\parskip}{0.5em}
\setlength{\parindent}{0em}

\begin{document}

\begin{center}
  {\LARGE \textbf{\myname}}\\[0.5em]
  \href{mailto:gustavo@luchetti.dev}{gustavo@luchetti.dev}\\
  \href{https://linkedin.com/in/gustaluchetti}{linkedin.com/in/gustaluchetti}
\end{center}


\section*{Experience}

\noindent
\begin{tabular*}{\linewidth}{@{\extracolsep{\fill}} l r }
  {\large\textbf{Nitro Química} | Jul/2023 - Present} & {\textit{São Paulo, Brazil}} \\
\end{tabular*}\\[0.2em]
\noindent\textbf{Digital Analyst}, Junior Digital Analyst
\begin{itemize}[leftmargin=*]
  \item Upgrade internal spreadsheet tooling (crucial in sales that amounted to
  \textbf{\textasciitilde R\$20MM} in 2023) into full-fledged web applications, enabling better
  access control, metrics and improved feature set.
  \item Incremental automation and streamlining of the onboarding process for new sales representatives, increasing visibility of the process company-wide.
\end{itemize}

\noindent
\begin{tabular*}{\linewidth}{@{\extracolsep{\fill}} l r }
  {\large\textbf{Source.ag} | Aug/2022 - Feb/2023} & {\textit{Amsterdam, Netherlands}} \\
\end{tabular*}\\[0.2em]
\noindent Implementation Analyst 
\begin{itemize}[leftmargin=*]
  \item Transform onboarding playbook into robust CLI process, decreasing errors and time to completion.
  \item Made possible for non-technical teams to do day-to-day database-related updates through a web interface (Retool).
\end{itemize}

\noindent
\begin{tabular*}{\linewidth}{@{\extracolsep{\fill}} l r }
  {\large\textbf{BTG Pactual Digital} | Jun/2021 - Jan/2022} & {\textit{São Paulo, Brazil}} \\
\end{tabular*}\\[0.2em]
\noindent Assistant Analyst, Intern Developer
\begin{itemize}[leftmargin=*]
  \item Development of new pages and better views/filters for backoffice web application.
  \item Maintenance of cloud endpoints, better logging and new functionalities.
\end{itemize}


\section*{Education}

\noindent
\begin{tabular*}{\linewidth}{@{\extracolsep{\fill}} l r }
  {\large\textbf{Utrecht University}} & {\textit{Utrecht, Netherlands}} \\
\end{tabular*}\\[0.2em]
\noindent Masters, Artificial Intelligence | Feb/2022 - Incomplete

\noindent
\begin{tabular*}{\linewidth}{@{\extracolsep{\fill}} l r }
  {\large\textbf{Escola Superior de Propaganda e Marketing}} & {\textit{São Paulo, Brazil}} \\
\end{tabular*}\\[0.2em]
\noindent Bachelors, Information Systems | Graduated Dec/2021 

\section*{Skills}

\begin{itemize}[leftmargin=*]
  \item \textbf{Full-Stack:} 4+ years of experience as a full-stack dev, having worked with
  Typescript, React, Angular, Python, and other languages.
  \item \textbf{DB \& Infrastructure:} Very confortable working with databases/SQL. Keen eye for
  proper schemas that take into account future growth.
  \item \textbf{Problem-Solving \& Adaptability:} Quickly adapt to new technologies and improve team
  workflows with automation. Not afraid to get into the terminal to figure things out.
  \item \textbf{Languages:} English (Fluent); Portuguese (Native)
\end{itemize}

\end{document}
